This chapter will provide the implementation details for individual nodes used in our BT algorithm. We will split these descriptions into BT nodes and auxiliary functions used in the nodes. We will also provide the implementation details for ROS nodes and other ROS-related parts.

\section{Behavior tree nodes}
    Here we will present the implementation of individual nodes in our algorithm. We will split the nodes into categories based on the sub-tree they belong to. We will also show the basic functionality of the library used.
    \subsection{Introduction}
        The BT algorithm is implemented using the behaviortree-cpp-v3 library. Therefore, we will present how we create, implement and start polling the tree. We will also show how nodes are created, implemented, and used.\\\\
        \bfc{Creating the node}\\
            To create the node, we need to create a class that inherits from one of the parent classes in the library. The parent classes depend on the type of node we want to create. If we create an action node, we inherit from the \texttt{SyncActionNode} class. If we create a condition node, we will inherit from the \texttt{ConditionNode} class.\\
            There are two mandatory functions for all nodes, the \texttt{tick} and \texttt{providedPorts} functions. These two functions must be implemented, or an error will occur.\\
            The \texttt{tick} function is responsible for the actual implementation of the node. It is called every time the node is polled. It is also responsible for returning the state of the node.\\
            The \texttt{providedPorts} function defines the ports the node will use. This function must be defined even if the node does not use any ports.\\\\
        \bfc{Using the node}\\
            To use a node, we must register it in the \texttt{BehaviorTreeFactory} object. We do this by calling the \texttt{registerNodeType} function. For this function, we need to specify the class of the node we want to register, e.g., one of the nodes we created. It also takes one \texttt{std::string} parameter, which identifies the name of the node in our BT algorithm \texttt{.xml} file.\\\\
        \bfc{Creating and running the tree}\\
            To create the tree, we first must have a \texttt{.xml} file with the tree structure. This file is then parsed by the \texttt{BehaviorTreeFactory} object using the \texttt{createTreeFromFile} function. The result is a \texttt{Tree} object which we can store and later run. Ahead of calling the parsing for the tree file, all the nodes used in the file must be registered.\\
            To run the tree, we call the \texttt{tickRoot} function on the \texttt{Tree} object. This function returns the state of the root node of the tree.\\\\
        \bfc{Blackboard}\\
            The blackboard is a shared memory between the nodes of the tree. It is used to store data that is being utilized by multiple nodes.\\
            It is also the reason why we implement the \texttt{providedPorts} function. This function specifies the ports the node will use. The ports can serve as an \texttt{input}, an \texttt{output}, or both. \texttt{Input} ports can take a constant value (specified in the \texttt{.xml} file of the tree structure) or look for a value in the blackboard.\\\\
        \bfc{Logging}\\
            The BT library also provides us with logging functionality. This functionality is useful for debugging and testing.\\
            We can use different types of loggers. The most common one is the \texttt{StdCoutLogger} which logs to the standard output. We can also use the \texttt{FileLogger}, which saves logs to a file.\\
            We will use the \texttt{FileLogger} to log the tree execution. This logger is useful for its integration with the \texttt{Groot} application as we can import the produced file and visualize the polling of our BT structure.\\
            The logging will be used only for debugging and testing purposes and serves no other function in the final product.
    \subsection{Main BT}
        In this BT, we only have one non-sub-tree node. This is because this sub-tree encodes the algorithm's structure rather than having nodes for execution.\\\\
        \bfc{StartAlgorithm -- Condition node}\\
            This node is responsible for determining whether the robot is in the phase of crossing the road during its mission. It is necessary to implement such a node to facilitate the transfer of control from path planning to road crossing. In contrast, we could determine if the crossing should start based on the distance of the robot from the road. However, this method would fail whenever our robot has to walk alongside any road.\\
            This node is implemented as a ROS service updating a static variable, which is checked when the node is ticked.\\
            This service should be used mainly by other nodes outside of the package itself, with one notable exception. The exception being the very last node of our tree. It serves as a prevention against the looping of our algorithm.
    \input{sections/Init_BT.tex}
    \input{sections/Perpendicular_BT.tex}
    \input{sections/Crossing_BT.tex}
    