\chapter{Libraries}
\label{sec:libraries}
    In this chapter we will specify the libraries we used in our code. We will provide a short description of the library alongside a link to the library and a specify the version we are using. We will divide the libraries by the programming language they are written for.

    \section{\CC\ libraries}
        \bfc{behaviortree-cpp-v3}\\
            This library provides us with the tools to implement and run a behavior tree. We used it in version 3.8.\\
            It is available at \url{https://github.com/BehaviorTree/BehaviorTree.CPP} and has two versions of documentation. The first one is older at \cite{BT_docs} and the second newer one is at \cite{BT_docs_new}.\\\\
        \bfc{GeographicLib}\\
            This library provides us with the tools to convert between different coordinate systems. We used it in version 2.2.\\
            It is available with documentation at \cite{GeographicLib}.

    \section{Python libraries}
        \bfc{Overpy}\\
            This library is used to access the OSM Overpass API. We used it in version 0.6.\\
            It is available at \url{https://github.com/DinoTools/python-overpy}.\\\\
        \bfc{Shapely}\\
            This library is used to work with geometric objects. We used it in version 1.8.2.\\
            Documentation for this library is available at \cite{shapely}.\\\\
        \bfc{Numpy}\\
            This library is used for mathematical operations and batch operations on data. We used it in version 1.22.4.\\
            More information alongside the library's documentation is available at \cite{numpy}.\\
        \bfc{Utm}\\
            This library provides bidirectional conversions between UTM and WGS84 coordinate systems. We used it in version 0.7.\\
            It is available at \url{https://github.com/Turbo87/utm}.
